---
title: "Zonebuilders"
subtitle: "Cross-platform and language-agnostic tools for generating zoning systems for urban analysis and modelling "  
author: "Robin Lovelace, Martijn Tennekes, Dustin Carlino, FOSS4G 2021"
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    nature:
      slideNumberFormat: "%current%"
      highlightStyle: github
      highlightLines: true
      ratio: 16:9
      countIncrementalSlides: true
---

```{r, eval=FALSE, echo=FALSE}
# see slides manually uploaded online: https://slopes-slides.netlify.app/slides.html#1
# to run these slides locally:
xaringan::inf_mr("data-raw/slides.Rmd")
```

```{r xaringanExtra, echo=FALSE}
# From https://github.com/gadenbuie/xaringanExtra
xaringanExtra::use_xaringan_extra(c("tile_view", "animate_css", "tachyons"))
```


```{r setup, include=FALSE}
library(tmap)
library(tidyverse)
tmap_mode("view")
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(
  fig.width=9, fig.height=3.5, fig.retina=3,
  out.width = "100%",
  # cache = TRUE,
  echo = FALSE,
  message = FALSE, 
  warning = FALSE,
  fig.show = TRUE,
  hiline = TRUE
)
```



```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_duo_accent(
  link_color = "blue",
  title_slide_background_color = "#FFFFFF",
  title_slide_background_size = "100%",
  title_slide_background_image = "zb_buenos_aires.png",
  title_slide_background_position = "bottom",
  title_slide_text_color = "#080808",
  primary_color = "#080808",
  secondary_color = "#FF961C",
  inverse_header_color = "#FFFFFF"
)
```

---

.left-column[

# Why?

- Every city has a different zoning system
- Need for consistency when doing inter-city comparisons
- Need for a general solution
- Existing 'zone-building' systems start with 'basic statistical units' (BSUs)
- Fun FOSS programming challenge!

]

--

.right-column[

## Available zones are often arbitrary

```{r, fig.height=6}
u = "https://geodata.lib.berkeley.edu/download/file/nyu-2451-34202-geojson.json"
f = "buenos_aires_official_zones.geojson"
# download.file(u, f)
zones_ba = sf::read_sf(f)
tm_shape(zones_ba) +
  tm_borders(lwd = 9) +
  tm_basemap(server = leaflet::providers$OpenStreetMap) +
  tm_scale_bar()
```


]

???

# Contents:

## Why slopes?

## Key functions

## Future plans


---


# Thanks

- Stephan Hügel and the GeoRust community for support with the Rust code
- The broadly defined R-Spatial community for making the R package possible

## Links

- [Paper](https://zonebuilders.github.io/zonebuilder/articles/paper.html) describing the ClockBoard zoning system, implemented with zonebuilders
- [zonebuilder R package](https://zonebuilders.github.io/zonebuilder) for building zones in R
- [zonebuilder Rust crate](https://crates.io/crates/zonebuilder) for building zones in Rust/anywhere 
- [zonebuilder web app](https://zonebuilders.github.io/zonebuilder-rust) for building zones in your browser
